---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---
```{r}
library(dplyr)

```
```{r}
library(psych)
setwd('C:\\Users\\Chaitanya Kannan\\Desktop\\SDA Lab')

```
Importing data which is in csv file
```{r}
pdata = read.csv('pizza_delivery.csv')


```

Printing Summary of data
```{r}
summary(pdata)
```
Printing first few rows of the data
```{r}
head(pdata)

```
Number of rows in dataset:
```{r}
nrow(pdata)

```
Number of columns in dataset:
```{r}
ncol(pdata)
```

Count total rows in data frame with no NA values in any column of
```{r}
nrow(na.omit(pdata))

```
Printing absolute frequencies of Branch attribute
```{r}
table(pdata$branch)
```
Printing relative frequencies of Branch attribute length(pdata$branch): Gives the number of rows in the data
```{r}
table(pdata$branch)/length(pdata$branch)

```
Printing ECDF of branch
```{r}
plot(ecdf(table(pdata$branch)), xlab="Branch", ylab="ECDF", main="ECDF plot for Branch", col=c('blue','green'))
plot(ecdf(pdata$temperature), xlab="Temperature", ylab="ECDF", main="ECDF plot for Temperature", col="blue")
barplot(table(pdata$branch), xlab="Branch", ylab="Count", main="Bar plot of Branch", col=c('#001199','#923','green'))
pie(table(pdata$branch), labels=names(table(pdata$branch)), main="Bar plot of Branch", col=c('#001199','red','green'))
hist(pdata$time)
hist(pdata$time,freq = TRUE)
plot(density(pdata$time, kernel = 'gaussian', bw = 0.5))
```
